---
title: "Template BeSD Report - COVID-19 Vaccination"
output: word_document
---

```{r, include = FALSE}

library(flextable)
library(dplyr)
```


# `r REPORT_TITLE`

## Background

Behavioural and social drivers of vaccination (BeSD) are “beliefs and experiences specific to vaccination that are potentially modifiable to increase vaccine uptake” [1]. The BeSD framework developed by the World Health Organization (WHO) groups these drivers into four domains [2]:

-   **Thinking and feeling** about vaccines and vaccine-preventable diseases
-   **Social processes** and norms that affect vaccine uptake
-   **Motivation** (or hesitancy) to seek vaccination
-   **Practical issues** involved in seeking and receiving vaccination, such as accessibility and cost

The BeSD data collection tools developed by WHO are designed to explore each of these domains.

*In this section, provide background information about the BeSD survey.*

## Methods

*Provide information about how data were collected:*

-   *Sample design*
-   *Age group included*

*Provide information on the survey instrument. Did the questions asked follow the BeSD standards exactly? Did any questions need to be standardized? Were additional questions/modules included?*

Data were analysed using the WHO’s freely available Behavioural and Social Drivers of Vaccination: Tools for Impact (BeSD-TI) software [3]. BeSD-TI is designed to facilitate flexible and rigorous analysis of BeSD surveys.

## Results

### Priority Indicators

The BeSD priority indicators for COVID-19 vaccination are:

-   **Confidence in vaccine benefits** (thinking and feeling): percentage of `r stringr::str_to_lower(COV_SURVEY_RESPONDENTS)` who say a COVID-19 vaccine is moderately or very important for their health
-   **Family norms** (social processes): percentage of `r stringr::str_to_lower(COV_SURVEY_RESPONDENTS)` who say most of their close family and friends want them to get a COVID-19 vaccine
-   **Intention to get child vaccinated** (motivation): percentage of `r stringr::str_to_lower(COV_SURVEY_RESPONDENTS)` who say they want to get a COVID-19 vaccine or are already vaccinated
-   **Knowing where to get vaccination** (practical issues): percentage of `r stringr::str_to_lower(COV_SURVEY_RESPONDENTS)` who say they know where to get a COVID-19 vaccine for themselves
-   **Affordability** (practical issues): percentage of `r stringr::str_to_lower(COV_SURVEY_RESPONDENTS)` who say that vaccination is moderately or very easy to pay for


```{r, results = 'asis', echo = FALSE}

for(i in 1:nrow(inputs_working)){
  input_i <- inputs_working[i,]
  
  sections_out <- list()
  
  if (!is.na(input_i$plot_path)){
    section_new <- knitr::knit_child(
      'besd_report_subsection_plot.rmd',
      envir = environment(), quiet = TRUE
    )
  } else {
    
    dat_i <- readRDS(input_i$rt_input_path) 
    
    section_new <- knitr::knit_child(
      'besd_report_subsection_table.rmd',
      envir = environment(), quiet = TRUE
    )
  }
  
  cat(unlist(section_new), sep = "\n")
}


```


## References

[1] World Health Organization. (2022). Understanding the behavioural and social drivers of vaccine uptake. WHO position paper – May 2022. Weekly Epidemiological Record vol. 97(20). <https://www.who.int/publications/i/item/who-wer9720-209-224>.

[2] World Health Organization. (2022). Behavioural and social drivers of vaccination: tools and practical guidance for achieving high uptake. <https://iris.who.int/handle/10665/354459>. License: CC BY-NC-SA 3.0 IGO

[3] World Health Organization and Biostat Global Consulting. (2024). Behavioural and Social Drivers of Vaccination: Tools for Impact (BeSD-TI). <https://github.com/BiostatGlobalConsulting/BeSDTI>
